Proposed Solution

### 2016-11-11 Ennan-Proposal/solutions.tex

\begin{figure}[!h]
%\begin{subfigure}{.3\textwidth}
%\begin{lstlisting}[mathescape=true]
%n = {}
%for (c in $C$):
%  n1 = M(c)
%  n = merge(n, n1)
%\end{lstlisting}
%\end{subfigure}%
\begin{subfigure}{.07\textwidth}
\underline{File 1}
\begin{lstlisting}[mathescape=true]
A
B
C
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.07 \textwidth}
\phantom{R}
\begin{lstlisting}[mathescape=true]
AB
AC
BC
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.1\textwidth}
\underline{File 2}
\begin{lstlisting}[mathescape=true]
A
C
B
\end{lstlisting}
\end{subfigure}%
\end{figure}
As an example of this process consider the situation where the training set contains two files, and the only rule we consider is ordering.
File 1 contains keywords in the order $[A,B,C]$, and file 2 contains the ordred keywords $[A,C,B]$.
File 1 will produce the set of possible rules $AB, BC, AC$ - and file 2 will produce $AC, CB, BC$.
The only rule that holds for all the files in the training set is then $AC$, so only that rule will be included.

@@

With a configuration file that has been verified against catastrophic
failures (\eg, missing entry, type, and ordering errors), 
the user may also want to examine more subtle issues.
Anomalous values can cause tricky, but impactful, performance and memory
issues that are hard to debug, as discussed in Example 4 of 
$\S$\ref{sec-motiv}. 
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

>>>>

\com{
\begin{figure}[!h]
%\begin{subfigure}{.3\textwidth}
%\begin{lstlisting}[mathescape=true]
%n = {}
%for (c in $C$):
%  n1 = M(c)
%  n = merge(n, n1)
%\end{lstlisting}
%\end{subfigure}%
\begin{subfigure}{.07\textwidth}
\underline{File 1}
\begin{lstlisting}[mathescape=true]
A
B
C
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.07 \textwidth}
\phantom{R}
\begin{lstlisting}[mathescape=true]
AB
AC
BC
\end{lstlisting}
\end{subfigure}%
\begin{subfigure}{.1\textwidth}
\underline{File 2}
\begin{lstlisting}[mathescape=true]
A
C
B
\end{lstlisting}
\end{subfigure}%
\end{figure}
}

As an example of this process, consider the situation 
where the training set contains two files F1 and F2, 
and the only rule we consider is ordering.
F1 contains keywords in the order $[A,B,C]$, 
and F2 contains the ordered keywords $[A,C,B]$.
F1 will produce the set of possible rules $AB, BC, AC$, 
and F2 will produce $AC, CB, BC$.
The only rule that holds for all the files in the training set is 
then $AC$, so only that rule will be included.

@@

With a configuration file that has been verified against catastrophic
configuration errors (\eg, missing entry, type, and ordering errors), 
the user may also want to examine some anomalous values,
which may also cause tricky and critical performance
issues that are hard to debug.
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.
